To log or not to log

### 2022-11-15 main.tex
Addressing co-author comments

Probabilistic forecasts play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as for example economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic and has been an important tool to inform public policy. Evaluating forecasts is important, as the evaluation provides feedback for forecasters and researchers necessary to improve their models, and it helps decision makers distinguish good from bad predictions and choosing forecasts that inform future decisions.

Proabbilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectaction, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. Two proper scoring rules commonly used in epidemiology and other fields are the Continuous Ranked Probability Score (CRPS) \citep{gneitingStrictlyProperScoring2007} and the Weighted Interval Score (WIS) \citep{bracherEvaluatingEpidemicForecasts2021}. Both the WIS and CRPS represent a measure of the absolute distance between the predictive distribution and observation and represent a generalisation of the absolute error to full predictive distributions (see details in the SI). The WIS can be thought of as an approxmiation of the CRPS for forecasts in a quantile format and has very similar properties (the WIS converges towards the CRPS for an increasing set of equally-spaced prediction intervals). Due to its widespread use in epidemiology (and its similarity to the CRPS) we mostly focus on the WIS in this paper, ignoring other proper scoring rules. Formulas for the WIS are given in the SI.

% Maybe insert WIS formula here?

Evaluating forecasts based on absolute errors (for simplicity we use the term interchangeably with absolute distance, even though the former technically only applies to point forecasts), as is done by the WIS, may not always be desirable, especially in an epidemiological context. 
% The reason for this is that generally, the way for ecasts are evaluated should correspond to the error structure of the model and the type of errors models will usually make.
Epidemiological processes are usually understood to be exponential in nature and therefore are most commonly described and modeled in multiplicative terms. Under the assumption that these models are correctly capturing the underlying inherent transmission dynamics, it would therefore make sense to focus evaluation on multiplicative, rather than absolute errors. Often, if the model is performing badly in multiplicative terms, this means that there is a flaw with its assumptions that needs to be resolved, regardless of performance in absolute terms. Evaluating epidemiological forecasts based on a measure of absolute error (as is common practice) can make it harder to diagnose and quantify model mis-specification. It also may make it more difficult to deal with the potential non-stationarity of epidemiological processes, or to compare performance across targets that are on very different orders of magnitudes (like for example cases and hospitalisations).

In this paper we argue that it may therefore be helpful to shift the focus of the evaluation on multiplicative, rather than absolute errors. This is approximately equal to scoring the growth rate of a forecast and can be achieved by transforming the forecasts as well as the observations using the logarithm before applying the WIS or CRPS. We focus on the log transformation, as it represents a very convenient way of achieving our goal of evaluating how well a forecast captures the growth dynamic inherent to epidemiological process. However, we note that the same logic we use can also applied to other transformations which could shift the focus of evaluation in different ways. For example, given an appropriate transformation, it could also be possible to evaluate forecasters based on the shape of the trajectory they predicted. It would even be possible to construct composite scores as a weighted sum of scores based on different transformations, allowing forecast consumers to assign explicit weights to different qualities of the forecasts.

In section [REF] we discuss the broader idea of transforming forecasts, and in section [REF] give a detailed theoretical of the log transformation and its interpretation. In section [REF] we present an applied example using forecasts submitted to the European COVID-19 Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. The European COVID-19 Forecast Hub is one of several Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021} that systematically collected, aggregated and evaluated forecasts of several COVID-19 targets created by different teams. Forecasts submitted to the COVID-19 Forecast Hubs are probabilistic in nature [Citation e.g. Held et al.], meaning that forecasters provide a full predictive distribution which quantifies their uncertainty. These predictive distributions are reported in the form of a set of 23 quantiles (11 symmetric prediction intervals as well as a median prediction). 
%Currently, the US Flu Forecasting Hub and COVID-19 Scenario Hubs in the US and in Europe use the same format.

@@

Applying the log transformation, among other transformations, is permissible because it is a strictly monotonic transformation. While rankings between different models may indeed change, even for a single forecast, the relevant condition for a scoring rule to be strictly proper is still satisfied: In expectation a forecaster will receive the best score if she reports a predictive distribution that is equal to the data-generating distribution, even after transforming both the forecasts and the observations (representing draws from the data-generating distribution).

@@

Unfortunately, the log transformation cannot readily be applied when dealing with negative or zero values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. Values of zero should potentially also be removed from the analsys, as it does not make sense to interpret relative errors on zero counts. Alternatively, if one is not willing to omit them, a small quantity (such as 1) could be added to all observations before taking the logarithm. Note that predictive distribtions have to be truncated in a similar way. When dealing with count data we could extend this argument to all small values (rather than just zeros), as it is hard to reliably evaluate relative errors when dealing with small discrete values. One could therefore decide to remove forecasts for small quantities below a certain threshold from the analysis.

\subsection{Scoring multplicative errors}

@@

This approximation breaks down when the difference between the predicted and the actual growth rate becomes too large (albeit forecasts are still evaluated in terms of relative errors). If this is of great concern one may want to use a different transformation like dividing forecasts and observations by the last known values instead in order to score the growth rate explicitly (although this lacks the elegance of having one single transformation per time point).

@@

\subsection{Effects on model rankings}
Rankings between different forecasts may be affected by applying the log transformation even when looking at a single forecast. As an example, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would equal the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.6}{0.9} = 1.06$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of her prediction interval, while only being slightly further away with the upper interval. This is likely to lead to a more lenient treatment of (one-sided) outlier forecasts.

Overall model rankings usually differ even more when performance is averaged across multiple forecasts. This effect is not mainly driven by the kinds of changes in model rankings for single forecasts we just discussed. Rather, aggregate scores across multiple forecasts are affected by the fact some scores will in general be much larger than others. On the natural scale, aggregate scores will usually be dominated by predictions of quantities with high absolute values. Even an ideal forecaster will make much larger errors when predicting a quantity such as reported case numbers, than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log transforming forecasts and observations may also result in the opposite extreme, since small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This is especially true when forecasts are restricted to discrete values. 
Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/SIM-mean-state-size.png}
    \caption{Simulation showing how the relationship between mean and variance of the forecast quantity affects scores. 1,000 samples were drawn from different negative binomial distributions and scores were computed assuming an ideal forecaster (forecast distribution equal to data-generating distribution). Observations were simulated for different means of the negative-binomial distributions (representing, for example, the number of cases in differently sized states) as well as different relationships between mean and variance (representing, for example, three different infectious processes). The variance of the negative binomial is given as $\sigma^2 = \mu + \mu^2 / \theta$, meaning that for large theta the negative binomial distribution is equal to the poisson distribution. We used values of $\theta = 0.1$ (red), 1 (green) and 1b (blue). To make the scores for the different distributios comparable, scores were normalised to one, meaning that the mean score for every distribution (red, green, blue) is one. 
    A: Normalised WIS for ideal forecasts with increasing means of three distribution with different relationships between mean and variance. B: Same plot as A with both axes log-transformed. MAYBE CAN GET RID OF B.}
    \label{fig:SIM-wis-state-size-mean}
\end{figure}

MAYBE MOVE TO SI. NEED TO ASK JOHANNES ABOUT IT. 
For simulated negative binomial count data, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. 
% To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

In the previous subsection we suggested to add a small number to all values in order to handle zeroes in the observations. While the choice of the number to add is somewhat arbitrary, it does have an influence on scores. By adding a number to forecasts as well as observations, measures of relative errors are slighly altered (while still preserving propriety of the score as we're applying a strictly monotonic transformation). Especially for forecasts of small values, the choice of the number that is added may affect scores quite strongly, as relative errors shrhink most for small quantities when adding a number. In principle, it is also possible to add a large number (e.g. 100 or 10,000) to all observations and forecasts in order to equalise relative errors between forecasts of different quantities if one finds that average scores are dominated too strongly by forecasts for small quantities.

@@

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Figure \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores also varied considerably across targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}. Both on the natural scale as well as on the log scale, scores increased considerably with increasing forecast horizon (see Figure \ref{fig:HUB-scores-horizon}). The increase was more pronounced for cases than for deaths. We hypothesise that this increase in scores across horizons represents the relative difficulty to forecast values into the future, which was noticeable both on the natural as well as the logarithmic scale.

@@

On the natural scale, scores correlate strongly (XX) with the average number of observed cases / deaths in a given country (see Fig \ref{fig:HUB-mean-locations}A, B). On the log scale, the correlation between average WIS and the mean number of observations in a country is much weaker and if anything tends to be slightly negative (giving higher weight to locations with few observations when averaging scores).

@@

When comparing examples of forecasts on the natural scale with log-transformed ones (see Figures XX, XX, XX) a few interesting patterns emerge. Missing the peak, i.e. predicting increasing numbers while actual observations are already falling, tends to contribute a lot to overall scores on the log scale (see forecasts in May in Figure XXA, B). On the log scale, these have less of an influence, as errors are smaller in relative terms (see panels C and D). We hypothesise that the larger divergence in scores for cases (compared to scores for deaths) displayed in Figure \ref{fig:HUB-cors}C is related to the fact that outlier forecasts missing the peak are more common for cases than for deaths. 
Conversely, failure to predict an upswing while numbers are still low, is not severely punished on the natural scale (see forecasts in July in Figure XX A, B), as overall absolute errors are low. On the log scale, missing lower inflection points tends to lead to more severe penalties (see panels C and D). One can also observe that on the natural scale, scores tend to track the overall level of the target quantity (compare for example forecasts for March-July with forecasts for September-October in Figure XXE, F). On the log scale, scores increase whenever forecasts are far away from the truth in relative terms, regardless of the overall level of observations. Furthermore, including very low numbers in the confidence intervals may lead to very high scores on the log-scale. This may be an issue especially when forecasting small quantities. Figure \ref{fig:HUB-model-comparison-baseline} shows forecasts and scores for the baseline model, which had zero included in its 50 percent intervals for the forecasts in XX to XX, leading to excessive dispersion values on the log scale. Notwithstanding the general concern, one can argue that in the specific example (at least for cases) including zero in the prediction intervals was unreasonable and rightly penalised given that case numbers were in the thousands.

@@

\paragraph{SAM}

COULD MAYBE ADD SOME ANALYSIS ABOUT WHAT KINDS OF MODELS BENEFITTED AND WHICH ONES GOT PENALISED MORE. AT THE MOMENT WE HAVE A VERY NICE FIGURE THAT ISN'T REALLY REFERENCED IN THE TEXT. SAM TO THE RESCUE!

@@

\paragraph{Other transformations - maybe move to Discussion}
While we focus on the log transformation in this paper, there are other transformations that may be helpful in an epidemiological context. One could for example divide all forecasts by the population in a location, to obtain forecasts standardised incidences per e.g. 100,000 inhabitants. 
Or one could apply a Box-Cox transformation MISSING. 
Or a square-root transformation MISSING. 
Or one could divide each forecast by the forecast of the previous week (and observations by the observation of the previous week), to transform preditions to week-to-week growth rates. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory. Note that this is not well defined in the context of forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate.

COULD ALSO BE DISCUSSION
Whether or not a log transformation is apprpriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \cite{bracherEvaluatingEpidemicForecasts2021} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high.

@@

>>>>

Probabilistic forecasts play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic, during which it has demonstrated the critical role it can play in informing public policy. Forecast evaluation is important, as it provides feedback for forecasters and researchers to improve their models, and it helps decision makers distinguish good from bad predictions and choosing forecasts that will inform future decisions.

Probabilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectation, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. 
This paper focuses on one particular proper scoring rule, the Weighted Interval Score (WIS, formulas given in Section XXX in the SI) \citep{bracherEvaluatingEpidemicForecasts2021}, which is commonly used in epidemiology and other fields. The WIS can be understood as an approximation of the Continuous Ranked Probability Score (CRPS) \citep{gneitingStrictlyProperScoring2007} for predictive distributions represented by a set of predictive quantiles. The WIS and the CRPS measure the absolute distance between the predictive distribution and the observed value and can be understood as a generalisation of the absolute error to full predictive distributions (see details in section XX in the SI). For simplicity, we will use "absolute error" and "absolute distance" interchangeably, even though the former applies only to point forecasts and the latter would be more appropriate for predictive distributions. 
The WIS has been used by several Forecast Hubs for COVID-19 in the US [CITATION], Europe [CItation], Germany and Poland [CITATION], as well as the US Flu Forecasting Hub and the Scenario Hubs in US and Europe and XX.

Evaluating forecasts based on the absolute distance between forecast and observed value may not always be optimal in an epidemiological context. Epidemiological processes are commonly understood and modeled to be inherently exponential in nature, as every infectious individual is assumed to lead to some number of additional infections [CITATION]. It would therefore seem more appropriate to focus the evaluation on errors on the multiplicative growth rate, rather than on absolute errors on the observed values, to better represent the underlying disease dynamics. Evaluating forecasts based on absolute errors in practice also means that scores are strongly influenced by the overall order of magnitude of the quantity to forecast. This makes it difficult compare predictive performance across time, given that epidemiological processes may be non-stationary, or to compare performance across targets that are on very different orders of magnitudes (for example cases and hospitalisations) [CITE KATH ECDC, and others].

In this paper, we discuss how log transforming the forecasts and observations prior to applying the WIS (or CRPS) may be an appropriate way to address the aforementioned issues with evaluating forecasts based on absolute errors. We first outline the motivation for transforming forecasts prior to scoring (section [REF]). We then provide a mathematical intuition of the impact of scoring on the log scale and its interpretation (section [REF]). We illustrate our findings on a series of examples using forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Finally, we give scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues on the use of transformed scores in the evaluation of infectious disease forecasts.

@@

Log transforming forecasts and observations shifts the focus of the evaluation while preserving propriety of the score. Instead of scoring the magnitude of absolute errors this approach captures relative errors and is approximately equivalent to scoring a forecast for the growth rate of the observed quantity.

We focus on the log transformation, as it represents a convenient way of achieving our goal of evaluating how well a forecast captures the growth dynamic inherent to epidemiological process.

Applying the log transformation, among other transformations, is permissible because it is a strictly monotonic transformation.

While rankings between different models may indeed change, even for a single forecast, the relevant condition for a scoring rule to be strictly proper is still satisfied: In expectation a forecaster will receive the best score if she reports a predictive distribution that is equal to the data-generating distribution, even after transforming both the forecasts and the observations (representing draws from the data-generating distribution).

@@

Unfortunately, the log transformation cannot readily be applied when dealing with negative or zero values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. One potential way to deal values of zero is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm as is common practice when log transforming counts. When dealing with count data we could extend this argument to all small values (rather than just zeros), as it is hard to reliably evaluate relative errors when dealing with small discrete values. An alternative solution is to remove forcasts for small, relative, values from ongoing analysis. In the following sections we will explore the implications of both of these strategies.

\subsection{Scoring multiplicative errors}

@@

This approximation breaks down when the difference between the predicted and the actual growth rate becomes too large (albeit forecasts are still evaluated in terms of relative errors). If this is of great concern one may want to use a different transformation such as dividing forecasts and observations by the last known values in order to score the growth rate explicitly (although this lacks the elegance of having one single transformation per time point).

@@

\subsection{Effects on model rankings}
Rankings between different forecasts may be affected by applying the log transformation even when looking at a single forecast. As an example, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would equal the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.6}{0.9}) = 1.06$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of her prediction interval, while only being slightly further away with the upper interval. This is likely to lead to a more lenient treatment of (one-sided) outlier forecasts.

Overall model rankings usually differ even more when performance is averaged across multiple forecasts. This effect is not mainly driven by the kinds of changes in model rankings for single forecasts we just discussed. Rather, as observations from exponential processes are likely to be on very different absolute scales, large observations will account for the majority of absolute score but will not dominate relative scores in the same way. When aggregating scores across metrices with different scales, for example reported cases, and hospitalisations even an ideal forecaster will make much larger errors when predicting a quantity such as reported case numbers, than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log transforming forecasts and observations may also result in the opposite extreme, since small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This is especially true when forecasts are restricted to discrete values. 
Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/SIM-mean-state-size.png}
    \caption{Simulation showing how the relationship between mean and variance of the forecast quantity affects scores. 1,000 samples were drawn from different negative binomial distributions and scores were computed assuming an ideal forecaster (forecast distribution equal to data-generating distribution). Observations were simulated for different means of the negative-binomial distributions (representing, for example, the number of cases in differently sized states) as well as different relationships between mean and variance (representing, for example, three different infectious processes). The variance of the negative binomial is given as $\sigma^2 = \mu + \mu^2 / \theta$, meaning that for large theta the negative binomial distribution is equal to the Poisson distribution. We used values of $\theta = 0.1$ (red), 1 (green) and 1b (blue). To make the scores for the different distributions comparable, scores were normalised to one, meaning that the mean score for every distribution (red, green, blue) is one. 
    A: Normalised WIS for ideal forecasts with increasing means of three distribution with different relationships between mean and variance. B: A but with log scale axis.}
    \label{fig:SIM-wis-state-size-mean}
\end{figure}

For simulated negative binomial count data, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. 
% To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

In the previous subsection we suggested to add a small number to all values in order to handle zeroes in the observations. While the choice of the number to add is somewhat arbitrary, it does have an influence on scores. By adding a number to forecasts as well as observations, measures of relative errors are slightly altered (while still preserving propriety of the score as we're applying a strictly monotonic transformation). Especially for forecasts of small values, the choice of the number that is added may affect scores quite strongly, as relative errors shrink most for small quantities when adding a number. In principle, it is also possible to add a large number (e.g. 100 or 10,000) to all observations and forecasts in order to equalise relative errors between forecasts of different quantities if one finds that average scores are dominated too strongly by forecasts for small quantities.

@@

PUT SOMEWHERE
The European COVID-19 Forecast Hub is one of several Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021} that systematically collected, aggregated and evaluated forecasts of several COVID-19 targets created by different teams. Forecasts submitted to the COVID-19 Forecast Hubs are probabilistic in nature [Citation e.g. Held et al.], meaning that forecasters provide a full predictive distribution which quantifies their uncertainty. These predictive distributions are reported in the form of a set of 23 quantiles (11 symmetric prediction intervals as well as a median prediction).

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Figure \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores also varied considerably across targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}). Both on the natural scale as well as on the log scale, scores increased considerably with increasing forecast horizon (see Figure \ref{fig:HUB-scores-horizon}). The increase was more pronounced for cases than for deaths. We hypothesise that this increase in scores across horizons represents the relative difficulty to forecast values into the future, which was noticeable both on the natural as well as the logarithmic scale.

@@

As expected on the natural scale, scores correlate strongly (XX) with the average number of observed cases / deaths in a given country (see Fig \ref{fig:HUB-mean-locations}A, B) and this relationship is not evident on the log scale. Interestingly, there is some evidence a negative relationship between the mean number of observations in a country and score when evaluated on a log scale implying that countries with lower mean incidence may be harder to forecast.

@@

When comparing examples of forecasts on the natural scale with log-transformed ones (see Figures XX, XX, XX) a few interesting patterns emerge. Missing the peak, i.e. predicting increasing numbers while actual observations are already falling, tends to contribute a lot to overall scores on the natural scale (see forecasts in May in Figure XXA, B). On the log scale, these have less of an influence, as errors are smaller in relative terms (see panels C and D). We hypothesise that the larger divergence in scores for cases (compared to scores for deaths) displayed in Figure \ref{fig:HUB-cors}C is related to the fact that outlier forecasts missing the peak are more common for cases than for deaths. 
Conversely, failure to predict an upswing while numbers are still low, is not severely punished on the natural scale (see forecasts in July in Figure XX A, B), as overall absolute errors are low. On the log scale, missing lower inflection points tends to lead to more severe penalties (see panels C and D). One can also observe that on the natural scale, scores tend to track the overall level of the target quantity (compare for example forecasts for March-July with forecasts for September-October in Figure XXE, F). On the log scale, scores increase whenever forecasts are far away from the truth in relative terms, regardless of the overall level of observations. Furthermore, including very low numbers in the confidence intervals may lead to very high scores on the log-scale. This may be an issue especially when forecasting small quantities. Figure \ref{fig:HUB-model-comparison-baseline} shows forecasts and scores for the baseline model, which had zero included in its 50 percent intervals for the forecasts in XX to XX, leading to excessive dispersion values on the log scale. Notwithstanding the general concern, one can argue that in the specific example (at least for cases) including zero in the prediction intervals was unreasonable and rightly penalised given that case numbers were in the thousands.

@@

Evaluating the rank order of forecasts from the ECDC forecast hub we saw that scoring after a log transform altered the order of forecast models as expected based on our simulated case study. In particular, we note that models that are known to not make use of a exponential error model and to be biased towards under-prediction, such the the MUNI-ARMA model were ranked lower when using a log transform. A submission by the authors of this study, the epiforecasts-EpiNow2 forecast model, was the most impacted by the change to log scale scoring moving from last place for reported cases to 4th place. This makes sense given that it explicitly models errors on an exponential scale, and is relatively unbiased meaning it may be over-penalised due to over-prediction during periods of peak incidence. Interestingly, other models that are growth rate based, such as the LANL-GrowthRate forecaster, do less well after a log-transform. Encouragingly for the ECDC forecast Hub the Hub ensemble, which is the forecast the organisers suggest forecast consumers make use of, remains one of the top forecasts across scoring schemes and indeed ranks higher for reported cases when a log transform is used.

@@

\paragraph{Other transformations}
While we focus on the log transformation in this paper, there are other transformations that may be helpful in an epidemiological context. One could for example divide all forecasts by the population in a location, to obtain forecasts standardised incidences per e.g. 100,000 inhabitants. 
Or one could apply a Box-Cox transformation MISSING. 
Or a square-root transformation MISSING. 
Or one could divide each forecast by the forecast of the previous week (and observations by the observation of the previous week), to transform preditions to week-to-week growth rates. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory. Note that this is not well defined in the context of forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate.

Whether or not a log transformation is appropriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \cite{bracherEvaluatingEpidemicForecasts2021} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high.

@@

NEEDS TO GO SOMEWHERE
However, we note that the same logic we use can also applied to other transformations which could shift the focus of evaluation in different ways. For example, given an appropriate transformation, it could also be possible to evaluate forecasters based on the shape of the trajectory [CITATION https://arxiv.org/abs/2209.04035] they predicted. It would even be possible to construct composite scores as a weighted sum of scores based on different transformations, allowing forecast consumers to assign explicit weights to different qualities of the forecasts.
